A Note on GMM Estimation of Theories of Expectation Formation

### 2019-10-24 notes/GMMResults.tex
Debugged the importing errors from GMMEst.But need to simplify the all_moments bools.

\documentclass[]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[a4paper,bindingoffset=0.2in,%
left=1.2in,right=1.2in,top=1.2in,bottom=1.2in,%
footskip=.25in]{geometry}

%opening
\title{Note on GMM Estimation of Theories of Expectation Formation}
\author{Tao Wang}

@@

\section{Generic Framework}

@@

\section{Estimation}
\subsection{Real-Time Data}

@@

\begin{figure}[ht]
\includegraphics[width=\textwidth]{figures/hist_rev_realtime.png}
\caption{Revisions of Current-vintage from Real-time Core CPI}
\label{real_time_rev}
	\begin{flushleft}
	{\footnotesize Note: real-time data  at time $t$ is defined the inflation from $t-1$ to $t$ according to the most recent vintage of CPI inflation at time $t$. The period is between 2000 M1-2018 M3.}
\end{flushleft}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=\textwidth]{figures/ts_rev_realtime.png}
	\caption{Current-vintage and Real-time Core CPI}
	\label{ts_real_time_current_vintage}
\end{figure}

@@

>>>>

\documentclass[]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[a4paper,bindingoffset=0.2in,%
left=1.2in,right=1.2in,top=1.2in,bottom=1.2in,%
footskip=.25in]{geometry}
\usepackage{caption}
\usepackage{subcaption}

%opening
\title{A Note on GMM Estimation of Theories of Expectation Formation}
\author{Tao Wang}

@@

\section{A Generic Framework}

@@

\section{Estimation}
\subsection{Real-time Data}

@@

\begin{figure}[ht]
		\centering
\includegraphics[width=0.7\textwidth]{figures/hist_rev_realtime.png}
\caption{Revisions of Current-vintage from Real-time Core CPI}
\label{real_time_rev}
	\begin{flushleft}
	{\footnotesize Note: real-time data  at time $t$ is defined the inflation from $t-1$ to $t$ according to the most recent vintage of CPI inflation at time $t$. The period is between 2000 M1-2018 M3.}
\end{flushleft}
\end{figure}

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.8\textwidth]{figures/ts_rev_realtime.png}
	\caption{Current-vintage and Real-time Core CPI}
	\label{ts_real_time_current_vintage}
\end{figure}

@@

\subsubsection{Professional Forecasters}

Figure \ref{SE_diag_SPF} and \ref{SE_diag_joint_SPF} plot the estimated moments for SE model together with the data moments professional forecasts of SPF.

From left to the right, the four columns of the figures are based on estimation

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of SE}
		\label{SE_diag_SPF}
		\includegraphics[width=0.24\textwidth]{figures/spf_se_est_diag0.png}
		\includegraphics[width=0.24\textwidth]{figures/spf_se_est_diag1.png}
		\includegraphics[width=0.24\textwidth]{figures/spf_se_est_diag2.png}
		\includegraphics[width=0.24\textwidth]{figures/spf_se_est_diag3.png}
	\end{subfigure}
	\vspace{1em}
	\vfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Joint Estimation of SE and Inflation Process}
		\label{SE_diag_joint_SPF}
	\includegraphics[width=0.24\textwidth]{figures/spf_se_est_joint_diag0.png}
	\includegraphics[width=0.24\textwidth]{figures/spf_se_est_joint_diag1.png}
	\includegraphics[width=0.24\textwidth]{figures/spf_se_est_joint_diag2.png}
	\includegraphics[width=0.24\textwidth]{figures/spf_se_est_joint_diag3.png}
	\end{subfigure}
	\\
	\begin{flushleft}
		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given. The bottom panel estimates the parameters of expectation formation and inflation process jointly. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, respectively. }
	\end{flushleft}
	\caption{SE of Professionals: Esimated Model Moments and Data Moments}
\end{figure}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of NI}
		\label{NI_diag_SPF}
		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_diag0.png}
		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_diag1.png}
		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_diag2.png}
		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_diag3.png}
	\end{subfigure}
	\vspace{1em}
	\vfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Joint Estimation of NI and Inflation Process}
		\label{NI_diag_joint_SPF}
		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_joint_diag0.png}
		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_joint_diag1.png}
		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_joint_diag2.png}
		\includegraphics[width=0.24\textwidth]{figures/spf_ni_est_joint_diag3.png}
	\end{subfigure}
	\\
	\begin{flushleft}
		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given. The bottom panel estimates the parameters of expectation formation and inflation process jointly. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, respectively. }
	\end{flushleft}
	\caption{NI of Professionals: Esimated Model Moments and Data Moments}
\end{figure}

\subsubsection{Households}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of SE}
		\label{SE_diag_SCE}
		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_diag0.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_diag1.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_diag2.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_diag3.png}
	\end{subfigure}
	\vspace{1em}
	\vfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Joint Estimation of SE and Inflation Process}
		\label{SE_diag_joint_SCE}
		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_joint_diag0.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_joint_diag1.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_joint_diag2.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_se_est_joint_diag3.png}
	\end{subfigure}
	\\
	\begin{flushleft}
		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given. The bottom panel estimates the parameters of expectation formation and inflation process jointly. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, respectively.}
	\end{flushleft}
	\caption{SE of Households: Esimated Model Moments and Data Moments}
\end{figure}

\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Estimation of NI}
		\label{NI_diag_SCE}
		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_diag0.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_diag1.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_diag2.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_diag3.png}
	\end{subfigure}
	\vspace{1em}
	\vfill
	\begin{subfigure}[b]{\textwidth}
		\centering
		\caption{Joint Estimation of SE and Inflation Process}
		\label{NI_diag_joint_SCE}
		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_joint_diag0.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_joint_diag1.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_joint_diag2.png}
		\includegraphics[width=0.24\textwidth]{figures/sce_ni_est_joint_diag3.png}
	\end{subfigure}
	\\
	\begin{flushleft}
		{\footnotesize Note: the upper panel estimates expectation formation only taking the process of inflation parameters as given. The bottom panel estimates the parameters of expectation formation and inflation process jointly. From left to the right, the moments used are $\overline y_{t|t}$, $\overline{FE}_{t}$, $\overline y_{t|t}$/$\overline{FE}_{t}$ and $\overline y_{t|t}$ / $\overline{FE}_{t}$/ $\overline{\textrm{Disg}_t}$, respectively. }
	\end{flushleft}
	\caption{NI of Households: Esimated Model Moments and Data Moments}
\end{figure}
